Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2023-12-20 demystify.tex
Updates from Overleaf

At GMU, we usually decide that a full-time PhD candidate is either (i) admit with funding (TA or RA, see \S\ref{sec:funding}) or (ii) rejected. In other words, in most cases, we either
admit you with full funding, or we reject your application. In some rare cases, we admit
without funding because you have funding on your own (e.g.,
supported by your government or having external grants). We also justify
our decision with a summary of your application, where we list
strengths (e.g., a well-known school) and weaknesses (e.g., weak
LORs).

@@

\paragraph{Waiving your Right to Review LORs}  Choosing not to look at a reference letter is pretty standard in school and job applications. When you waive your right to see the letter, it adds a layer of trust, showing you're confident in your choice of referees and that you're not trying to twist their words. It's also about keeping things open and honest between you and your letter writers, and encourages them to be real about your strengths and qualifications. Plus, it keeps things private.

@@

\paragraph{Reminding Writers to Submit Letters} After you submit your application, you can tell your writers that and remind them to submit their letters if they haven't done so. But don't send too many reminders as that can be annoying to the writers.

@@

\section{Preparing Materials}
\subsection{Sharing spreadsheets}
Many students use a spreadsheet to help them and their letter writers to keep track of their applications. You can create a personal and a shared spreadsheet but a simplest one is just a shared one (e.g., using Google sheet).  Here are some information to put on the sheet.  
\begin{itemize}
\item \textbf{Your info}: Full name, email, phone, link to website/CV).  This is helpful for the writers just in case they want to quickly get some information about you.
\item \textbf{Applications details}: University, Dept, Application System URL, Submission Deadlines, Application Status (e.g., submitted,  rejected, wait-listed, accepted)
\item \textbf{LoRs}: Writer 1, Writer 2, Writer 3.  If this is a shared document, you might want to omit names and just use writer X. Under each is their status, e.g., sent/not yet/reminder needed, etc.
\end{itemize}

>>>>

At GMU, we usually decide that a full-time PhD candidate is either (i) admit with funding (TA or RA, see \S\ref{sec:funding}) or (ii) rejected. In other words, in most cases, we either
admit you with full funding, or we reject your application. In some rare cases, we admit
without funding because you have funding on your own, e.g.,
supported by your government or having external fellowships. We also justify
our decision with a summary of your application, where we list
strengths (e.g., a well-known school) and weaknesses (e.g., weak
LORs).

@@

\paragraph{Waiving your Right}  Choosing not to look at a reference letter is pretty standard in school and job applications. When you waive your right to see the letter, it adds a layer of trust, showing you're confident in your choice of referees and that you're not trying to twist their words. It's also about keeping things open and honest between you and your letter writers, and encourages them to be real about your strengths and qualifications. Plus, it keeps things private.

@@

\paragraph{Reminding Writers} After you submit your application, you can tell your writers that and remind them to submit their letters if they haven't done so. But don't send too many reminders as that can be annoying to the writers.

@@

\section{Preparing and Tracking Applications}

\paragraph{Shared Spreadsheet} Many students use a spreadsheet to help them and their letter writers to keep track of their applications. They often use a shared spreadsheet (e.g., using Google Docs or Sheets).  Here are some information to put on the sheet.  
\begin{itemize}
\item \textbf{Your info}: Full name, email, phone, link to website/CV).  This is helpful for the writers just in case they want to quickly get some information about you.
\item \textbf{Applications details}: University, Dept, Application System URL, Submission Deadlines, Application Status (e.g., submitted,  rejected, wait-listed, accepted)
\item \textbf{LoRs}: Writer 1, Writer 2, Writer 3.  If this is a shared document, you might want to omit names and just use writer X. Under each is their status, e.g., sent/not yet/reminder needed, etc.

You can then share this sheet with your reference writers and remind them to submit LoRs on your behalf (see \S\ref{sec:lor}).
\end{itemize}

%\paragraph{Communicating with LoR writers and People Who Support You}

%stressfull time, rely on support from others
%ask ppl to review your SOPs
%provide information for LORs, ..
%
